data processing

### 2024-03-11 scRNAseq/processing.Rmd
fixed IDs

- K456985_PBMC
- K783496_PBMC
- K693104_PBMC
- K955601_PBMC
- P1_1_PBMC 
- P1_2_PBMC
- P3_1_PBMC
- P3_2_PBMC
- P8_1_PBMC
- P8_2_PBMC 
- P22_1_PBMC
- P22_2_PBMC
- P23_1_PBMC
- P23_2_PBMC
- P25_1_PBMC
- P25_2_PBMC
- P27_1_PBMC
- P27_2_PBMC
- P28_1_PBMC
- P28_2_PBMC
- P22_P23_K783496_CD4
- P8_P3_K456985_CD4
- P27_P28_K693104_CD4
- P12_1_PBMC
- P12_2_PBMC
- P26_1_PBMC
- P26_2_PBMC
- K496398_PBMC
- P12_P26_K496398_CD4

```{r get_data}
samples <- c('K456985_PBMC','K783496_PBMC','P1_1_PBMC','P22_1_PBMC','P22_P23_K783496_CD4','P23_2_PBMC','P25_2_PBMC','P27_2_PBMC',
             'P28_1_PBMC','P3_1_PBMC','P8_1_PBMC','P8_P3_K456985_CD4','K693104_PBMC','K955601_PBMC','P1_2_PBMC','P22_2_PBMC',
             'P23_1_PBMC','P25_1_PBMC','P27_1_PBMC','P27_P28_K693104_CD4','P28_2_PBMC','P3_2_PBMC','P8_2_PBMC',
             'P12_1_PBMC','P12_2_PBMC','P26_1_PBMC','P26_2_PBMC','K496398_PBMC','P12_P26_K496398_CD4')

>>>>

- HC-1_PBMC
- HC-5_PBMC
- HC-2_PBMC
- HC-3_PBMC
- IBD-1_1_PBMC 
- IBD-1_2_PBMC
- IBD-9_1_PBMC
- IBD-9_2_PBMC
- IBD-10_1_PBMC
- IBD-10_2_PBMC 
- IBD-3_1_PBMC
- IBD-3_2_PBMC
- IBD-4_1_PBMC
- IBD-4_2_PBMC
- IBD-5_1_PBMC
- IBD-5_2_PBMC
- IBD-7_1_PBMC
- IBD-7_2_PBMC
- IBD-8_1_PBMC
- IBD-8_2_PBMC
- IBD-3_IBD-4_HC-5_CD4
- IBD-10_IBD-9_HC-1_CD4
- IBD-7_IBD-8_HC-2_CD4
- IBD-2_1_PBMC
- IBD-2_2_PBMC
- IBD-6_1_PBMC
- IBD-6_2_PBMC
- HC-4_PBMC
- IBD-2_IBD-6_HC-4_CD4

```{r get_data}
samples <- c('HC-1_PBMC','HC-5_PBMC','IBD-1_1_PBMC','IBD-3_1_PBMC','IBD-3_IBD-4_HC-5_CD4','IBD-4_2_PBMC','IBD-5_2_PBMC','IBD-7_2_PBMC',
             'IBD-8_1_PBMC','IBD-9_1_PBMC','IBD-10_1_PBMC','IBD-10_IBD-9_HC-1_CD4','HC-2_PBMC','HC-3_PBMC','IBD-1_2_PBMC','IBD-3_2_PBMC',
             'IBD-4_1_PBMC','IBD-5_1_PBMC','IBD-7_1_PBMC','IBD-7_IBD-8_HC-2_CD4','IBD-8_2_PBMC','IBD-9_2_PBMC','IBD-10_2_PBMC',
             'IBD-2_1_PBMC','IBD-2_2_PBMC','IBD-6_1_PBMC','IBD-6_2_PBMC','HC-4_PBMC','IBD-2_IBD-6_HC-4_CD4')
